

\section*{References}
\begin{enumerate}
  % --- PAPERS ---
  \item \href{https://ieeexplore.ieee.org/document/986127}{\textbf{P. W. Shor} – Algorithms for Quantum Computation: Discrete Logarithms and Factoring. \textit{Proceedings 35th Annual Symposium on Foundations of Computer Science}, IEEE, 1994.}
  \item \href{https://ieeexplore.ieee.org/document/365700}{\textbf{D. Deutsch and R. Jozsa} – Rapid Solution of Problems by Quantum Computation. \textit{Proceedings of the Royal Society of London A}, 1992.}
  \item \href{https://theory.cs.princeton.edu/complexity}{\textbf{S. Arora and B. Barak} – Computational Complexity: A Modern Approach. Princeton University Press, 2009.}
  \item \href{https://oaktrust.library.tamu.edu/bitstreams/0c4096c3-69d5-47af-ae7f-848309a9c0ca/download}{\textbf{Kristopher Lonnie Watkins} – An Exposition on Peter Shor’s Polynomial-Time Factoring Algorithm and Its Effects on Post-Quantum Cryptography.}
  \item \href{https://www.classiq.io/insights/shors-algorithm-explained}{\textbf{Classiq Technologies} – Quantum Cryptography – Shor’s Algorithm Explained.}
  \item \href{https://www.classiq.io/insights/quantum-algorithms-shors-algorithm}{\textbf{Classiq Technologies} – Quantum Algorithms: Shor’s Algorithm.}

  % --- WIKIPEDIA / ONLINE ARTICLES ---
  \item \href{https://en.wikipedia.org/wiki/Shor%27s_algorithm}{\textbf{Wikipedia} – Shor’s Algorithm.}
  \item \href{https://en.wikipedia.org/wiki/BQP}{\textbf{Wikipedia} – BQP.}
  \item \href{https://en.wikipedia.org/wiki/Hadamard_gate}{\textbf{Wikipedia} – Hadamard Gate.}
  \item \href{https://en.wikipedia.org/wiki/Quantum_Fourier_transform}{\textbf{Wikipedia} – Quantum Fourier Transform.}
  \item \href{https://en.wikipedia.org/wiki/Euclidean_algorithm}{\textbf{Wikipedia} – Euclidean Algorithm.}
  \item \href{https://www.quantum-inspire.com/hadamard-gate/}{\textbf{Quantum Inspire} – Hadamard Gate.}

  % --- YOUTUBE / VIDEO SOURCES ---
  \item \href{https://www.youtube.com/watch?v=g_IaVepNDT4}{\textbf{Veritasium} – How Does a Quantum Computer Work?}
  \item \href{https://www.youtube.com/watch?v=zNzzGgr2mhk}{\textbf{Veritasium} – How to Make a Quantum Bit?}
  \item \href{https://www.youtube.com/watch?v=5_56TXtFVK4}{\textbf{Quantum Soar} – Quantum Computing Course: 3.8 Shor’s Algorithm.}

\end{enumerate}
