% ============================================================
%  front/editorial.tex — Editor's Address
% ============================================================
\clearpage
\thispagestyle{frontmatter}

\vspace*{0.5cm}

\begin{center}
  {\LARGE\bfseries\color{cmjcrimson}Editor's Address}\label{art:address}
\end{center}

\vspace{0.3cm}
\noindent\textcolor{cmjgold}{\rule{\textwidth}{1.2pt}}
\vspace{0.3cm}

\noindent Dear reader,

\vspace{0.25cm}

It is with great pleasure that we present the inaugural edition of the
{\color{cmjcrimson}\textit{Constructor Mathematical Journal}}, the student journal of the
Constructor University Mathematics Society.

\vspace{0.25cm}

This journal was born from a desire to give undergraduate researchers a venue
to communicate their work and to foster a culture of mathematical inquiry at
Constructor University Bremen. Each article collected here originated in our
Mathematics Undergraduate Seminar (UgS) and has been developed into an expository
piece intended to be accessible to a wide audience.

\vspace{0.25cm}

In its very-first volume, the {\color{cmjcrimson}CMJ} proudly presents to you
three excellent articles,

\begin{itemize}[leftmargin=1.5em, itemsep=0.3em]
  \item \textbf{Shannon's Theorem and Polar Codes} explores the foundations
        of reliable communication laid by Claude Shannon and traces the path
        to Erdal Ar{\i}kan's breakthrough construction of polar codes.
  \item \textbf{Bragg's Law in the Context of Protein Structure Determination}
        traces back to W.\,L.\ Bragg's 1913 discovery, on to the modern protein structure
        determination pipeline, illustrating how the prior enables the recovery of atomic-scale structure
        from diffraction data.
  \item \textbf{The Qubit and Shor's Algorithm} provides a step-by-step
        journey from the basics of quantum computing to Peter Shor's
        celebrated factoring algorithm and its implications for modern
        cryptography.
\end{itemize}

\vspace{0.1cm}

As I sign-off as Editor-in-Chief, I am excited to see how this journal evolves in
the coming years. To the seminarists, I invite you to pass on the torch to the next generation
of students, to explore fascinating mathematics through the UgS, to share that same fascination
through the {\color{cmjcrimson}CMJ}. To the students, I encourage you to get involved in this exciting venture
that is the UgS. There you will always find a place to be curious, to ask questions, to make mistakes 
and learn from them, to grow as a mathematician, and most importantly, as a person.

The {\color{cmjcrimson}CMJ} is a testament to the mathematical excellence of those who
contributed to it, and to the potential of those courageous enough to try. 
May it transcend the brevity of our time and echo softly in the spaces we leave behind.

\vspace{0.4cm}

\noindent\textit{Yours Sincerely, }\\
\textbf{Omar Elshinawy --- MATH'25}\\
Editor-in-Chief of the \textcolor{cmjcrimson}{CMJ}
\vspace{0.15cm}

\noindent\textcolor{cmjgold}{\rule{\textwidth}{1.2pt}}

\vspace{0.6cm}