% ============================================================
%  front/info.tex — Journal information, submission guidelines,
%                   editorial board, and recorded talks
% ============================================================
\clearpage
\thispagestyle{frontmatter}

% \vspace*{1cm}

% \begin{center}
%   {\LARGE\bfseries\color{cmjcrimson}About This Journal}
% \end{center}

% \vspace{0.2cm}
% \noindent\textcolor{cmjgold}{\rule{\textwidth}{1.2pt}}
% \vspace{0.6cm}

\def\internal{0.3cm}
\def\external{0.7cm}

% Two-column layout for this page
\begin{minipage}[t]{0.47\textwidth}

  {\large\bfseries\color{cmjcrimson}The Journal}

  \vspace{\internal}

  The \textit{Constructor Mathematical Journal} {\color{cmjcrimson}{(\textbf{CMJ})}} is the
  undergraduate mathematics journal of Constructor University Bremen, published
  bi-annually by the Mathematics Society at Constructor University (MSCU).

  \vspace{0.4cm}

  The {\color{cmjcrimson}{CMJ}} publishes expository and research articles written by undergraduate students. All articles originate in the MSCU's own Mathematics
  Undergraduate Seminar (UgS) and are developed into self-contained expositions,
  accessible to a broad mathematical audience.

  \vspace{\external}
  
  {\large\bfseries\color{cmjcrimson}Recorded Talks}

  \vspace{\internal}

  Each article in the {\color{cmjcrimson}{CMJ}} is accompanied by a recorded talk delivered
  at the UgS. The recordings are freely
  available and provide an accessible entry point to each paper's ideas.

  \vspace{\internal}

  \noindent\href{https://elshenawyom.github.io/teaching/ugs}{\texttt{elshenawyom.github.io/teaching/ugs}}

  \vspace{\external}

      {\large\bfseries\color{cmjcrimson}Editorial Board}

  \vspace{\internal}

  \noindent
  \begin{tabular}{@{}l@{}}
    \textbf{Editor-in-Chief}\\
    Omar Elshinawy\,---\,{\color{cmjgray}MATH'25}\\[0.3cm]
    % \textbf{Managing Editor}\\
    % XXX\,---\,{\color{cmjgray}MAJOR'YEAR}\\[0.3cm]
    % \textbf{Associate Editors}\\
    % XXX\,---\,{\color{cmjgray}MAJOR'YEAR} \\
    % XXX\,---\,{\color{cmjgray}MAJOR'YEAR}\\[0.3cm]
    \textbf{Faculty Advisor}\\
    Prof. Dr. Keivan Mallahi-Karai %\,---\,Name \textit{\color{cmjgray}\small(Constructor University)}\\
  \end{tabular}

    \vspace{\external}

      {\large\bfseries\color{cmjcrimson}Cover Art}

    Bragg's Law on a
    protein crystal lattice (left) reflects the rays that determine
    its structure; a Bloch sphere represents the qubit (centre) that is a 
    superposition of ones and zeroes; and a channel polarization tree 
    (right) freezes channels into reliable and unreliable ones to realise 
    Shannon's capacity.
\end{minipage}
\hfill
\begin{minipage}[t]{0.47\textwidth}

  {\large\bfseries\color{cmjcrimson}Submission Guidelines}

  \vspace{\internal}

  We welcome submissions from students at Constructor University and from
  visiting students who have participated in the UgS.
  Manuscripts should:
  \begin{itemize}[leftmargin=1.2em, itemsep=0.2em]
    \item be written in \LaTeX\ using the \texttt{cmj} style package
          (available at the journal website);
    \item include an abstract of 80--150 words;
    \item be self-contained and aimed at an undergraduate audience;
    \item include a complete reference list.
  \end{itemize}

  %\vspace{\internal}

  To participate in the Mathematics Undergraduate Seminar (UgS), there is a simple application 
  process. One simply attends to a member of the MSCU board, possible through
  the respective contact channels, or closely follows the MSCU's latest
  announcements.
  % \vspace{0.2cm}
  % \noindent\texttt{XXX\,---\,math.constructor.university/cmj}

  \vspace{\external}

    {\large\bfseries\color{cmjcrimson}Contact}

  \vspace{\internal}
  \textbf{Address.}\\
  Constructor University \\
  Campus Ring 1\\
  28759 Bremen\\
  Germany\\[0.2cm]
  \textbf{Email.}\\
  \href{mailto:constructor.maths@gmail.com}{
    \texttt{maths-society@constructor.university}
    }\\[0.2cm]
  \textbf{Main Site.}\\
  \href{https://math.constructor.university/}{
    \texttt{https://math.constructor.university}
  }\\[0.2cm]
  \textbf{Undergraduate Site.}\\
  \href{https://constructor-math.github.io/Home Page/landing.html}{
    \texttt{https://constructor-math.github.io}
    }\\

  \vspace{\external}

  \noindent\textcolor{cmjgold}{\rule{\textwidth}{1.2pt}}

  \noindent{\small\color{cmjgray}%
  \textcopyright\ 2025 Constructor University Mathematics\\ Society.
  All rights reserved. \hfill}

\end{minipage}

\vspace{0.8cm}
\noindent\textcolor{cmjgold}{\rule{\textwidth}{1.2pt}}
