% ============================================================
%  front/editorial.tex — Editor's Address
% ============================================================
\clearpage
\thispagestyle{frontmatter}

\vspace*{0.5cm}

\begin{center}
  {\LARGE\bfseries\color{cujblue}Editor's Address}\label{art:address}
\end{center}

\vspace{0.3cm}
\noindent\textcolor{cujgold}{\rule{\textwidth}{1.2pt}}
\vspace{0.3cm}

\noindent Dear reader,

\vspace{0.25cm}

It is with great pleasure that we present the inaugural edition of the
\textit{Constructor Mathematical Journal}, the student journal of the
Constructor University Mathematics Society.

\vspace{0.25cm}

This journal was born from a desire to give undergraduate researchers a venue
to communicate their work and to foster a culture of mathematical inquiry at
Constructor University Bremen. Each article collected here originated in our
Mathematics Undergraduate Seminar (UgS) and has been developed into an expository
piece intended to be accessible to a wide audience.

\vspace{0.25cm}

In this first volume you will find three articles spanning information theory,
coding theory, quantum computation, and mathematical biology:

\begin{itemize}[leftmargin=1.5em, itemsep=0.3em]
  \item \textbf{Shannon's Theorem and Polar Codes} explores the foundations
        of reliable communication laid by Claude Shannon and traces the path
        to Erdal Ar{\i}kan's breakthrough construction of polar codes.
  \item \textbf{The Qubit and Shor's Algorithm} provides a step-by-step
        journey from the basics of quantum computing to Peter Shor's
        celebrated factoring algorithm and its implications for modern
        cryptography.
  \item \textbf{Bragg's Law and X-Ray Crystallography} \textit{(description
        placeholder --- to be completed once the third article is finalised).}
\end{itemize}

\vspace{0.1cm}

As I sign-off as the Editor-in-Chief, I am excited to see how this journal evolves in
the coming years. To the UgS seminarists, I invite you to pass on the torch to the next generation
of students, to explore fascinating mathematics through the UgS, to share that same fascination
through the CMJ. To the students, I encourage you to get involved in this exciting venture
that is the UgS. There you will always find a place to be curious, to ask questions, to make mistakes 
and learn from them, to grow as a mathematician, and most importantly, as a person.

The CMJ is a testament to the mathematical excellence of those who
contributed to it, and to the potential of those courageous enough to try. 
May it transcend the brevity of our time and echo softly in the spaces we leave behind.

\vspace{0.4cm}

\noindent\textit{Yours Sincerely, }\\
\textbf{Omar Elshinawy --- MATH'25}\\
Editor-in-Chief of the \textcolor{cujred}{CMJ}
\vspace{0.15cm}

\noindent\textcolor{cujgold}{\rule{\textwidth}{1.2pt}}

\vspace{0.6cm}