% ============================================================
%  front/info.tex — Journal information, submission guidelines,
%                   editorial board, and recorded talks
% ============================================================
\clearpage
\thispagestyle{frontmatter}

\vspace*{1cm}

\begin{center}
  {\LARGE\bfseries\color{cujblue}About This Journal}
\end{center}

\vspace{0.2cm}
\noindent\textcolor{cujgold}{\rule{\textwidth}{1.2pt}}
\vspace{0.6cm}

% Two-column layout for this page
\begin{minipage}[t]{0.47\textwidth}

  {\large\bfseries\color{cujblue}The Journal}

  \vspace{0.3cm}

  The \textit{Constructor Mathematical Journal} (\textbf{CMJ}) is the
  undergraduate mathematics journal of Constructor University Bremen, published
  annually by the Constructor University Mathematics Society (CUMS).

  \vspace{0.4cm}

  CMJ publishes expository and research articles written by undergraduate and
  graduate students. All articles originate in the CUMS Mathematics
  Undergraduate Seminar and are developed into self-contained expositions
  accessible to a broad mathematical audience.

  \vspace{0.7cm}

  {\large\bfseries\color{cujblue}Editorial Board}

  \vspace{0.3cm}

  \noindent
  \begin{tabular}{@{}l@{}}
    \textbf{Editor-in-Chief}\\
    XXX\,---\,Name \textit{\color{cujgray}\small(Constructor University)}\\[0.3cm]
    \textbf{Managing Editor}\\
    XXX\,---\,Name \textit{\color{cujgray}\small(Constructor University)}\\[0.3cm]
    \textbf{Associate Editors}\\
    XXX\,---\,Name \textit{\color{cujgray}\small(Constructor University)}\\
    XXX\,---\,Name \textit{\color{cujgray}\small(Constructor University)}\\[0.3cm]
    \textbf{Faculty Advisor}\\
    XXX\,---\,Name \textit{\color{cujgray}\small(Constructor University)}\\
  \end{tabular}

  \vspace{0.7cm}

  {\large\bfseries\color{cujblue}Contact}

  \vspace{0.3cm}

  Constructor University Mathematics Society\\
  Campus Ring 1, 28759 Bremen, Germany\\[0.2cm]
  \texttt{XXX@constructor.university}\\
  \texttt{XXX\,---\,math.constructor.university}

\end{minipage}
\hfill
\begin{minipage}[t]{0.47\textwidth}

  {\large\bfseries\color{cujblue}Submission Guidelines}

  \vspace{0.3cm}

  We welcome submissions from students at Constructor University and from
  visiting researchers who have participated in the CUMS seminar.
  Manuscripts should:

  \begin{itemize}[leftmargin=1.2em, itemsep=0.2em]
    \item be written in \LaTeX\ using the \texttt{cumsj} style package
          (available at the journal website);
    \item include an abstract of 80--150 words;
    \item be self-contained and aimed at an undergraduate audience;
    \item include a complete reference list.
  \end{itemize}

  \vspace{0.3cm}

  Submissions and enquiries may be sent to the editorial address above.
  The journal website provides the article template, style guide, and
  submission portal:

  \vspace{0.2cm}
  \noindent\texttt{XXX\,---\,math.constructor.university/cmj}

  \vspace{0.7cm}

  {\large\bfseries\color{cujblue}Recorded Talks}

  \vspace{0.3cm}

  Each article in this volume is accompanied by a recorded talk delivered
  at the CUMS Mathematics Undergraduate Seminar. The recordings are freely
  available and provide an accessible entry point to each paper's ideas:

  \vspace{0.3cm}

  \noindent\texttt{XXX\,---\,math.constructor.university/talks}

  \vspace{0.3cm}

  The talks are typically 30--45 minutes and are aimed at students with a
  solid background in first-year undergraduate mathematics. All recordings
  are hosted on the university's streaming platform and may be accessed
  without registration.

  \vspace{0.7cm}

  {\large\bfseries\color{cujblue}About the cover}

  \vspace{0.3cm}

  The cover combines artistic elements from each article: Bragg's Law and a
  crystal lattice (left), a Bloch sphere representing the qubit (centre), and
  a small channel polarization tree (right). A subtle translucent overlay and
  shared colour palette visually blend the three panels and emphasise the
  thematic links between physical structure, information theory, and quantum
  computation.

  \vspace{0.7cm}

  {\large\bfseries\color{cujblue}Acknowledgements}

  \vspace{0.3cm}

  The editors thank the Constructor University Mathematics Department for
  their generous support, and all seminar participants whose questions and
  discussions shaped the final articles.

\end{minipage}

\vspace{0.8cm}
\noindent\textcolor{cujgold}{\rule{\textwidth}{1.2pt}}
