\clearpage
\thispagestyle{frontmatter}

\vspace*{0.5cm}

\begin{center}
  {\LARGE\bfseries\color{cujblue}On the CMJ's First Volume}\label{art:volume}
\end{center}

\vspace{0.3cm}
\noindent\textcolor{cujgold}{\rule{\textwidth}{1.2pt}}
\vspace{0.3cm}

  %     {\large\bfseries\color{cujblue}Journal Cover}

  %     \vspace{0.3cm}

  % The cover combines artistic elements from each article. 
  % A subtle translucent overlay and
  % shared colour palette visually blend the three panels and emphasise the
  % thematic links between physical structure, information theory, and quantum
  % computation.

      {\large\bfseries\color{cujblue}A Short Story}

      \vspace{0.3cm}

      The Mathematics Undergraduate Seminar (UgS) is a tradition of student research and exposition,
      first introduced as part of the MATH curriculum. This tradition has persisted for years on, 
      until the Spring of 2024. The MATH programme was restructured into an MMDA\footnote{Mathematics, Modeling \& Data Analytics} variant,
      and the seminar was discontinued.\\[0.3cm]
      As a seminarist myself, this tradition is encoded in Constructor (well, Jacobs...) University's mathematical DNA. 
      A discontinuation in itself would be a step backwards for its mathematics society. So, we relaxed the curricular condition and took the
      seminar outside the classroom. The UgS was therefore reborn as a student-led initiative, attracting a superset of mathematics and non-mathematics students.\\[0.3cm]
      In its incarnation, the seminar is now a thriving hub of mathematical exploration, bringing students and faculty closer than ever before.  
      This journal is the fruit of this rebirth.

      \vspace{0.5cm}

      {\large\bfseries\color{cujblue}An Honourable Mention}
  
      \vspace{0.3cm}

  It is our honour and pleasure to 
  acknowledge the following {\color{cujgray}(MATH'27)} students,
  \begin{itemize}
    \item \textbf{Klesta Qehaja}, for her work on \emph{Random Walks in $\mathbb Z^d$},
    \item \textbf{Pablo Santos Guerrero}, for his work on \emph{Piccard-Vessiot Theory and Liouville's Theorem},
    \item \textbf{Vano Kakiashvili}, for his work on \emph{the Legendary 1988 IMO Problem Six} .
  \end{itemize}
  Despite not accumulating into full articles, their contributions 
  to the Mathematics Undergraduate Seminar (UgS) are nothing short of excellent. 
  The inauguration of this journal would not be possible without you. 

  \vspace{0.3cm}

  {\large\bfseries\color{cujblue}Acknowledgements}

  \vspace{0.3cm}

  We would like to express our sincere gratitude to the Mathematics faculty, for the warm support
  and encouragement. In particular, we thank Prof. Dr. Keivan Mallahi-Karai, for peerlessly advising
  this volume and for his unwavering support of the UgS\@. Worthy of mention is Dr. Ivan Ovsyannikov, for both his academic and moral 
  contributions to the seminarists. It means a lot for us students. 
  
\newpage