% ============================================================
%  articles/01-shannon.tex
%  Shannon's Theorem and Polar Codes — Aly Assaf
% ============================================================
\label{art:shannon}

\articleheader
  {Shannon's Theorem and Polar Codes}
  {Aly Assaf}
  {Electrical and Computer Engineering, Class of 2027\\Constructor University Bremen}
  {Coding Theory is responsible for facilitating reliable message-passing
   over communication channels.  In 1948, Claude Shannon proved that for
   every channel there exists a family of error-correcting codes that allow
   reliable communication at any rate below the channel's capacity.
   Shannon's work is, however, non-constructive, as it provides no method
   to design such efficient codes.  While there have been attempts over the
   years to reach this theoretical capacity, notably with LDPC codes (1990)
   and Turbo Codes (1993), these could only empirically approach the
   theoretical limit.  This stood for 60 years until Erdal Ar{\i}kan's
   introduction of Polar Codes, the first clean and mathematically proven
   family of codes to achieve Shannon's maximum capacity over symmetric
   binary-input memoryless channels.  This expository paper aims to briefly
   introduce the general Coding Theory scheme, outline the key ideas in
   Shannon's arguments, and explore Ar{\i}kan's outstanding construction of
   polar codes.}

% ── Article body (original sections) ───────────────────────

\input{assets/papers/shannon-polar-codes/sections/1-fundamentals}

\input{assets/papers/shannon-polar-codes/sections/2-linearcodes}

\input{assets/papers/shannon-polar-codes/sections/3-codingproblem}

\input{assets/papers/shannon-polar-codes/sections/4-shannontheorem}

\input{assets/papers/shannon-polar-codes/sections/5-polarcodes}

% ── Conclusion ─────────────────────────────────────────────
\section{Conclusion \& Final Remarks}

We've followed in the footsteps of one of the greatest revolutionaries that
built the foundations of reliable and efficient communication---Claude
Shannon.  By exploring coding and information theory, we not only built our
understanding on a number of underlying concepts but also developed a bird's
eye view on how Ar{\i}kan took the teachings of Shannon to a practical
application to the benefit of humanity.  The ingenuity and experimentation
that Ar{\i}kan expressed during his development of Polar Codes is an
impressive and satisfying learning experience.

Shannon's Theorem is a beautiful mathematical construct that creates a clear
guideline for engineers to build on.  Polar Codes are the practical
realisation of this.  They are an incredible tool in the engineer's arsenal
that allows optimised communication under the correct circumstances.

% ── References ─────────────────────────────────────────────
\articlereferences

\begin{enumerate}[label={[\arabic*]}, leftmargin=2em, itemsep=0.25em]

\item P.~Elias, ``Error-Free Coding,''
      \textit{IRE Trans.\ Inform.\ Theory}, vol.~4, no.~4,
      pp.~29--37, 1954.

\item V.~Guruswami and A.~Rudra, ``Proof of Shannon's Theorem and an
      Explicit Code,'' Lecture~4, \textit{CSE 533: Error-Correcting Codes},
      Carnegie Mellon University, Oct.\ 2006.

\item V.~Guruswami and D.~Halperin, ``More on Linear Codes,''
      Lecture~2, \textit{CSE 533: Error-Correcting Codes},
      Carnegie Mellon University, Oct.\ 2006.

\item V.~Guruswami and W.~Machmouchi, ``Shannon's Theorem,''
      Lecture~3, \textit{CSE 533: Error-Correcting Codes},
      Carnegie Mellon University, Oct.\ 2006.

\item V.~Guruswami and V.~Rastogi, ``Error Correcting Codes,''
      Lecture~1, \textit{CSE 533: Error-Correcting Codes},
      Carnegie Mellon University, Oct.\ 2006.

\item L.~Slot and S.~Zur, ``Shannon's Noisy-Channel Coding Theorem,''
      Vrije Universiteit Amsterdam, Feb.\ 2015.

\item M.~Goemans, ``Shannon's Noisy Coding Theorem,''
      18.310 Lecture Notes, MIT, May 2015.

\item S.~Biswas, ``Introduction to Coding Theory: Basic Codes and
      Shannon's Theorem,'' Undergraduate Research Paper, UChicago, 2011.

\item M.~Sudan and M.~Suzgun, ``A Gentle Introduction to Polar Codes,''
      Lecture~8, \textit{CS 229r: Information Theory in Computer Science},
      Harvard University, Jan.\ 2019.

\item O.~Elshinawy, ``Syllabus \& Agenda: Mathematics Undergraduate
      Seminar,'' Spring 2025.

\end{enumerate}

\vspace{0.15cm}

\noindent\textcolor{cmjgold}{\rule{\textwidth}{1.2pt}}

\vspace{0.6cm}

\newpage