% ============================================================
%  articles/02-shor.tex
%  The Qubit and Shor's Algorithm — Ahmed Maghri
% ============================================================
\label{art:shor}

\articleheader
  {The Qubit and Shor's Algorithm: A Step-by-Step Exploration}
  {Ahmed Maghri}
  {Constructor University Bremen}
  {Shor's algorithm presents a polynomial-time quantum solution to the
   integer factorisation problem, threatening classical encryption protocols
   like RSA\@.  This article introduces the mathematical and computational
   foundations required to understand the algorithm, including modular
   arithmetic, continued fractions, and quantum principles.  We provide a
   step-by-step breakdown of Shor's algorithm and its quantum subroutine,
   emphasising accessibility and conceptual clarity, while also addressing
   practical constraints in current quantum hardware.  This article aims to
   make the concepts of Shor's algorithm accessible to readers with limited
   background in mathematics and quantum computing, while maintaining
   mathematical rigour and conceptual depth throughout.}

% ── Acknowledgements ──────────────────────────────────────
\vspace{0.3cm}
\noindent{\small\textbf{\color{cujblue}Acknowledgements.}\ %
I would like to sincerely thank Omar Elshinawy, head of the Mathematics
Society at Constructor University, for his valuable guidance and support
throughout the research and writing of this article.  I also wish to thank
Muaz Hussein, a first-year ECE major, for providing the first reviews and
constructive feedback on the manuscript.  A heartfelt thanks goes to my
mathematics and computer science professors and fellow Math Society members,
whose enthusiasm and insight made this research journey both enriching and
enjoyable.  Finally, and most importantly, I express my deepest gratitude to
my parents, without whom none of this would have been possible.}
\vspace{0.6cm}

% ── Article body (original sections, renamed to remove spaces) ──

\setcounter{section}{-1}

\input{assets/papers/qubit-shor/sections/00-preliminaries}

\input{assets/papers/qubit-shor/sections/01-intro-cryptography}

\input{assets/papers/qubit-shor/sections/02-quantum-computing}

\input{assets/papers/qubit-shor/sections/03-shor-algo}

\input{assets/papers/qubit-shor/sections/04-final-thought}

% ── References ────────────────────────────────────────────
\articlereferences

\begin{enumerate}[label={[\arabic*]}, leftmargin=2em, itemsep=0.25em]

\item P.\,W.~Shor, ``Algorithms for Quantum Computation: Discrete
      Logarithms and Factoring,'' \textit{Proc.\ 35th Annual Symposium
      on Foundations of Computer Science}, IEEE, 1994.

\item D.~Deutsch and R.~Jozsa, ``Rapid Solution of Problems by Quantum
      Computation,'' \textit{Proc.\ Royal Society of London~A}, 1992.

\item S.~Arora and B.~Barak, \textit{Computational Complexity: A Modern
      Approach}, Princeton University Press, 2009.

\item K.\,L.~Watkins, ``An Exposition on Peter Shor's Polynomial-Time
      Factoring Algorithm and Its Effects on Post-Quantum Cryptography.''

\item Classiq Technologies, ``Quantum Cryptography --- Shor's Algorithm
      Explained.''

\item Classiq Technologies, ``Quantum Algorithms: Shor's Algorithm.''

\item Wikipedia, ``Shor's Algorithm.''

\item Wikipedia, ``BQP\@.''

\item Wikipedia, ``Hadamard Gate.''

\item Wikipedia, ``Quantum Fourier Transform.''

\item Wikipedia, ``Euclidean Algorithm.''

\item Quantum Inspire, ``Hadamard Gate.''

\item Veritasium, ``How Does a Quantum Computer Work?'' (video).

\item Veritasium, ``How to Make a Quantum Bit?'' (video).

\item Quantum Soar, ``Quantum Computing Course: 3.8 Shor's Algorithm''
      (video).

\end{enumerate}
